A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-16 paper/ms.tex
change tablename
add new figure to tex

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{deltaXH_Tc_violins.png}
  \caption{Difference in abundances of this pair and other binary pairs in
    \citealt{2016ApJS..225...32B}.
    Additionally, we show the distribution of abundance difference
    between stars with similar metallicity difference
    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
    as violins with medians indicated by black line segments
    by randomly pairing up single stars at two metallicity bins similar to
    the pair of interest.
    The difference is always relative to the lower-$[\elem{Fe}/\elem{H}]$ star.
  }
  \label{fig:deltaXH}
\end{figure}
